% John D. Duncan, III
% feel free to use this as a template for your own resume/cv

\documentclass[11pt]{article}

\usepackage[margin=0.6in,bottom=0.5in]{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}

% underline for section titles
\titleformat{\section} {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.9pt]}]

% no indentation for first line of paragraphs
\setlength{\parindent}{0pt}

% https://texblog.org/2008/10/16/lists-enumerate-itemize-description-and-how-to-change-them/
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$\diamond$}
\renewcommand{\labelitemiv}{$\ast$}

\begin{document}
% header
\fancyfoot{}
\lhead{\textit{John D. Duncan, III}\hfill \thepage}
\pagestyle{fancy}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{center}
	{\huge \textbf{John D. Duncan, III}}
\end{center}
Software Engineer @ Quorum Analytics
\hfill
(240) 688-7187

1111 19th Street NW
\hfill
\texttt{\href{mailto:duncan+jobs@quorum.us}{duncan+jobs@quorum.us}}

Washington, DC 20036 \hfill \texttt{\url{https://github.com/JohnDDuncanIII}}
\hfill

\section*{Letter of Recommendation \hfill Charles W. Kann, III}

January 14th, 2019\\

Dear GW Department of Computer Science,\\

It is with great enthusiasm that I am writing to you today to recommend \textbf{Charles W. Kann, III} for the position of \textit{Computer Science Professor of Practice} at George Washington University. Throughout my own time as an undergraduate student, and into my professional career, it has become clear to me that Professor Kann's position as a Computer Science educator is not just a job, but a true \textbf{passion}. This passion manifests itself in multiplicities, a few of which I have detailed for you below.

\begin{itemize}
	\item Between his open door policy and pleasant \& sociable manner, Charles Kann is a \textbf{highly approachable} educator who goes \textbf{above and beyond} the call of duty to ensure that his students get all of the help they need to \textbf{succeed}. Professor Kann forges \textbf{personal connections} with all students, even outside of the department's prescribed office hours. In fact, his office, at one point, became a public forum for CS discourse between many of the more involved students in the major.
	
\begin{itemize}
	\item This aforementioned hospitality \textbf{transcends} the confines of the academic building, as Professor Kann invites alumni over for barbecues, picnics, holidays, skiing trips, and other social events in order to both keep up with and foster \textbf{lifelong friendships} and connections. Professor Kann, who is the only non-tenured adjunct faculty member in the department, is also the \textbf{only} professor from the Gettysburg Computer Science Department that does this.
\end{itemize}

	\item Charles Kann is a highly \textbf{versatile} Computer Science professor, capable of teaching \textbf{introductory} courses for non-majors, to teaching \textbf{mid-level} data structures courses, to teaching some of the more \textbf{advanced} assembly language and hardware theory courses. 

	\item Charles Kann is \textbf{selfless}, dedicating much of his time outside of the classroom to writing \textbf{free} and \textbf{open source textbooks} that are distributed publicly on the internet. Two of those, \href{https://cupola.gettysburg.edu/cgi/viewcontent.cgi?article=1000\&context=oer}{Digital Circuit Projects: An Overview of Digital Circuits Through Implementing Integrated Circuits} and \href{https://cupola.gettysburg.edu/cgi/viewcontent.cgi?article=1001\&context=oer}{MIPS Assembly Language Programming}, have each been downloaded tens of thousands of times.

	\item Charles Kann consistently offers undergraduate students the opportunity to work with him on \textbf{research projects} over the summer. One such project, that I worked on during the summer of my sophomore year, directly helped me get an internship working on disaster relief software with the Humanitarian Assistance and Disaster Relief Systems Group (44) at Massachusetts Institute of Technology's Lincoln Laboratory (MIT LL) in Lexington, Massachusetts the following summer.
	
\end{itemize}

I could go on, but in the interest of brevity, I will conclude here. I have every confidence that Charles Kann will make an excellent \textit{Computer Science Professor of Practice} at George Washington University. If you have any questions or require any further information, I have included my professional contact information above.\\

Best regards,
\\\\\\
John Duncan\\

\end {document}
