% John D. Duncan, III
% feel free to use this as a template for your own resume/cv

\documentclass[11pt]{article}

\usepackage[margin=0.6in,bottom=0.5in]{geometry}
\usepackage{dirtytalk}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{titlesec}

% underline for section titles
\titleformat{\section} {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.9pt]}]

% no indentation for first line of paragraphs
\setlength{\parindent}{0pt}

% https://texblog.org/2008/10/16/lists-enumerate-itemize-description-and-how-to-change-them/
\renewcommand{\labelitemi}{$\bullet$}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$\diamond$}
\renewcommand{\labelitemiv}{$\ast$}

% custom spacing for bullets
%\setlist[itemize]{leftmargin=0.35in, topsep=0pt} % label={}, noitemsep,

\begin{document}
% header
\fancyfoot{}
\lhead{\textit{John D. Duncan, III}\hfill \thepage}
\pagestyle{fancy}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\begin{center}
	{\huge \textbf{John D. Duncan, III}}
\end{center}
Home Address
\hfill
Phone Number

Home Address
\hfill
\texttt{\href{mailto:duncanjdiii+jobs@googlemail.com}{duncanjdiii+jobs@googlemail.com}}

\texttt{\url{https://github.com/JohnDDuncanIII}}
\hfill
\texttt{\url{https://dataswamp.org/~john/}}

\section*{Work Experience}
\textbf{\href{https://www.quorum.us/}{Quorum Analytics}}
\hfill
1050 Connecticut Avenue NW, Washington, DC

\textit{Software Engineer II} {\small (60 hours/week)}
\hfill
\textit{September 2020 - Present}
\hfill

\textit{Software Engineer}
\hfill
\textit{March 2018 - September 2020}
\hfill

\begin{itemize}
	\item Developing code that collects, interprets, organizes, and 
presents legislative and user-generated data on the Quorum SaaS platform.
	\begin{itemize}[noitemsep]
		\item Wrote the \textbf{Dashboards} feature \hfill full stack, pair
		\item Upgraded to \textbf{React 16} and \textbf{Enzyme 3} \hfill frontend, independent
		\item Wrote the \textbf{Committee/Presidential Transcripts} feature \hfill frontend, independent
		\item Wrote the \textbf{Bulk Actions} feature \hfill full stack, independent
		\item Wrote most of the client-facing portion of the \textbf{International} product \hfill frontend, independent
		\item Re-wrote and now independently maintain \textbf{Search} \hfill full stack, pair
		\item \textbf{Legacy bug fixes/enhancements}, \textbf{deployment}, \textbf{on-call}, dev-ops, \hfill full stack
		\item Served as \textbf{onboarding mentor} to two full stack engineers and an engineering manager.
		\item \textbf{Interviews} (phone/onsite, technical/design), ``\textbf{Learning Lab}'' presentations, organization of weekly dev-team \textbf{social events}
	\end{itemize}
\end{itemize}

\textbf{Massachusetts Institute of Technology: Lincoln Laboratory (MIT LL)}
\hfill
Lexington, MA 

\textit{Software Engineering Research Intern} {\small (40 hours/week)}
\hfill
\textit{Summer 2016}

\begin{itemize}
	\item Worked with the Humanitarian Assistance and Disaster Relief Systems Group \href{https://www.ll.mit.edu/mission/division4.html#gp44}{(Division 4 Group 44)} on the \href{https://www.dhs.gov/publication/national-hurricane-program-technology-modernization-local-evacuation-alert-verification}{\textbf{Local Evacuation Alert Verification}} (LEAV) program for \href{https://www.dhs.gov/publication/national-hurricane-program-technology-modernization-hurrevac-extended-hv-x}{\textbf{HURREVAC-eXtended}} (HVX). Wrote and designed an \textbf{Android application} for end users (LEAV) and a \textbf{JavaScript} (EXT-JS) module for the Emergency Manager front-end (HVX). Agile development cycle. Participated in a DHS defense workshop. Applied for DoD Secret Clearance. \href{https://docs.google.com/presentation/d/1d6u7eK2fBJElrRpEn1KlkTfReKO_tHj5iCAGb6vgtmg/}{Slides} and Supervisor's Assessment available upon request.
%	\begin{itemize}[noitemsep]
%		\item \textbf{Centralized} all continental U.S. evacuation zones into one database.
%		\item \textbf{Reduced} WFS-T call size by multiple orders of magnitude.
%		\item Gave a final \textbf{presentation} to the broader Group 44. 
%		\item The FEMA/DHS sponsor for the project was pleased with the final outcome.
%		\item \href{https://docs.google.com/presentation/d/1d6u7eK2fBJElrRpEn1KlkTfReKO_tHj5iCAGb6vgtmg/}{Slides} and Supervisor's Assessment available upon request.
%	\end{itemize}
\end{itemize}

\textbf{Gettysburg College Computer Science Department, Lakewood Country Club, SysArc, Dominos}
\hfill

\textit{Internship/Work Experience}
\hfill
\textit{2009-2016}

%\textbf{Gettysburg College Computer Science Department}
%\hfill
%Gettysburg, PA

%\textit{Software Engineering Research Intern}
%\hfill
%\textit{Summer 2015}
%
%\begin{itemize}
%	\item Worked with Professor Chuck Kann developing a Gettysburg Monuments \textbf{Android} application (published to the Google Play Store) and \textbf{website}. 
%\end{itemize}

%\textbf{Lakewood Country Club}
%\hfill
%Rockville, MD

%\textit{Outdoor Services}
%\hfill
%\textit{Summer 2014}

%\begin{itemize}
%\item[] Maintained driving range, ensured operation of carts, and cleaned member clubs \& bags. \\
%\end{itemize}

%\textbf{SysArc}
%\hfill
%Rockville, MD

%\textit{Intern}
%\hfill
%\textit{Summer 2012}

%\begin{itemize}
%\item[]  Helped troubleshoot technology issues with client user accounts and maintained servers. \\
%\end{itemize}

%\textbf{Domino's Pizza}
%\hfill
%Potomac, MD

%\textit{Insider}
%\hfill
%\textit{2009-2013}

%\begin{itemize}
%\item[]  Worked part-time while in High School training new hires, processing phone calls, preparing orders, and operating the cash register. Team Member of the Period PD13 12.
%\end{itemize}

%end section

\section*{Technical}
\begin{tabular}{ l l }
  	\textbf{Languages} & \textbf{JavaScript}, \textbf{Python}, \textbf{Go} \\
  	% & Some Java, C++, C, Mips ASM, Scheme R5RS, Emacs Lisp, and Visual Basic. \\

  	\textbf{Databases} & \textbf{PostgreSQL}, CockroachDB \\
  	
  	\textbf{Web} & \textbf{React}, \textbf{ES5/6}, \textbf{HTML5}, \textbf{CSS3} (Styled Components, Stylus), \textbf{DOM}, XUL, XPCOM \\
  	
  	\textbf{Tools} & \textbf{Git},  \textbf{Sublime Text}, \textbf{Emacs}, \textbf{GIMP}, \textbf{Regex}, \textbf{\LaTeX}, Blender, irc, Jira \\
  	
  	\textbf{Unix/Plan9} & \textbf{macOS}, \textbf{Darwin/XNU}, OpenBSD, plan9port, 9front, GNU/Linux, Android \\
  	& \textbf{Sh}, \textbf{Sed}, Awk, Grep, Rc \\
  	& XQuartz, pkg-src, homebrew, macports, ffmpeg, cygwin \\
  	\textbf{Images/3d} & html/svg $\Rightarrow$ png/jpeg/svg/pdf conversion, \textbf{xface}, xbm, xpm, blit ikon, base64, picons, ogre3d \\
\end{tabular}
\begin{itemize}
	%\item Competent using UNIX-like systems, the command line interface, system configuration, and shell scripting.
	\item Disclosed two bugs in the Gettysburg Campus Navigation Portal (CNAV) electronic record keeping system. The first allowed any user to \textbf{delete} any other \textbf{user account} from a CNAV `group' (mailing list). The second \textbf{leaked} all internal account images to the web. Received a cash award.
\end{itemize}
%end section

\section*{Side Projects (\url{http://cs.gettysburg.edu/~duncjo01/assets/portfolio.html})}
\begin{itemize}[noitemsep]
	\item \href{https://github.com/JohnDDuncanIII/MessageFaces}{\textbf{messagefaces}}: XUL/XPCOM add-on that displays popular \& recondite `face' images from email headers.
	\item \href{https://dataswamp.org/~john/assets/scripts/weather.js}{\textbf{weather}}: JavaScript on my homepage that displays a 7-day weather forecast using art that I made.
	\item \href{https://github.com/JohnDDuncanIII/faces}{\textbf{faces}}: Go library that converts an XFace to PNG and performs picon lookups from a picon database.
	\item \textbf{\href{https://github.com/JohnDDuncanIII/blog}{blog}/\href{https://github.com/JohnDDuncanIII/wiki}{wiki}}: Go micro-(blogging/wiki) platform.
	\item \textbf{\href{https://github.com/JohnDDuncanIII/macfonts}{macfonts}}: Converted all `80s resource fork Macintosh fonts to data fork fonts for use on macOS. 
	\item \href{https://github.com/JohnDDuncanIII/PokerSquares}{\textbf{pokersquares}}: Designed/wrote an Android app that uses an Expectimax \href{https://www.aaai.org/ocs/index.php/AAAI/AAAI16/paper/view/12537/12191}{NARL} AI player. 
	\item \href{https://github.com/JohnDDuncanIII/redlight}{\textbf{redlight}}: Designed/wrote an Android app that uses an \href{http://cs.gettysburg.edu/~tneller/papers/fowlplay.pdf}{ANN} AI player for the game of Pig.
	\item \href{https://github.com/JohnDDuncanIII/hog}{\textbf{hog}}: Managed and designed/wrote an Android app that plays a modified version of the game of Pig. 
	%\item \textbf{monuments}: Ported my \href{https://github.com/JohnDDuncanIII/dataswamp/tree/master/sites/monuments}{JS web app}, which maps points on the Gettysburg battlefield, to Android.
	%\item \textbf{design}: Designed UIs, sites, cursors, (p)icons, cards, a 3x4 font, and mac platinum \& mozilla xfpe themes.
	\item \href{https://github.com/KittyKatt/screenFetch/blob/master/screenfetch.1\#L126}{\textbf{screenfetch}}: Ported the popular system information script to macOS.
	\item \href{http://cs.gettysburg.edu/~duncjo01/archive/}{\textbf{archive}}: Archived many esoteric patterns, bitmaps, clip art, screensavers, and fonts from 1973-1999.
\end{itemize}
%end section

\section*{Education}
\textbf{\large{B.S. in Computer Science {\footnotesize Honors (3.60)} and Philosophy {\footnotesize Honors (3.73)}}}
\hfill
\href{https://www.gettysburg.edu/commencement/2017/pdfs/2017\%20Commencement\%20Program\%20FINAL.pdf}{\textit{May 2017}}


Gettysburg College, Gettysburg, PA \\

\href{https://www.gettysburg.edu/academic-programs/computer-science/programs/honors-programs}{Outstanding Computer Science Student} Award \hfill \textit{Class of 2017}

Eisenhower Institute Undergraduate Fellow 
\hfill
\textit{2016-2017}

Dean's Honors List \hfill \textit{Fall 2015/2016, Spring 2017}

Dean's Commendation List \hfill \textit{Fall 2013}

\subsection*{\underline{Computer Science}}
\textbf{Capstone} \textit{Adam's Wellness Family Connection Website Team Project} \hfill Adviser: Dr. Rod Tosten
\begin{itemize}[noitemsep]
	\item Presented \textbf{seven colloquia} to the department and broader Gettysburg community.
	\item Represented the Computer Science Department during the \textbf{Spring 2016 Get Acquainted Day}. 
	\item Organized \& facilitated two \say{\textbf{Hour of Code}} sessions for local students in the Adams County area.
	\item Led \textbf{three teams} that completed Android applications (two of which were published).
\end{itemize}

\subsection*{\underline{Philosophy}}
\textbf{Thesis} \textit{Virtual Futures: Virtuality as Political Praxis} \hfill Adviser: Dr. Lisa Portmess

\textbf{Capstone} \textit{Infinite Horizons: The World to Mind Question} \hfill Adviser: Dr. Daniel DeNicola
\begin{itemize}[noitemsep]
	\item Co-moderated a Philosophy Department \textbf{Socratic Club Seminar} about the future of work.
	\item Writing samples available upon request.
\end{itemize}

\subsection*{\underline{Eisenhower Institute Undergraduate Fellow}}
Program offers a select group of eight Gettysburg College students the chance to develop their \textbf{leadership skills} and knowledge \& understanding of \textbf{public policy}. Our research focus was refugee policy and our adviser was \textbf{Dr. Shirley Anne Warshaw}, Harold G. Evans Chair of Eisenhower Leadership Studies.
\begin{itemize}
	\item Researched and wrote the `New Technologies' section for our \href{https://www.state.gov/s/partnerships/ppp/diplab/}{\textbf{State Department Diplomacy Lab}} \href{https://drive.google.com/file/d/0B5fjh9FZOHSYT1dhVF8yYmd4UEk/view?usp=sharing}{White Paper} on \textbf{Health Care Records} in \textbf{Mixed-Migration settings}. We presented our findings to the \textit{Office of Economic Security, International Health and Biodefense Population, Refugees, and Migration} at the State Department. 
	\begin{itemize}
		\item Physical research for this project included: a trip to the United Nations, dinners, and in person meetings with experts in Europe and resettled Syrian refugees in Pennsylvania.
	\end{itemize}
	\item Co-organized and moderated \href{http://cs.gettysburg.edu/~duncjo01/assets/media/EI_panel_f16.pdf}{two} \href{http://cs.gettysburg.edu/~duncjo01/assets/media/EI_panel_s17_second.pdf}{panels} that detailed current issues in \textbf{public policy}, \textbf{national security}, \textbf{civics}, and \textbf{refugee rights}. 
	\item Gave a presentation detailing our research to the \textbf{EINAC} (Eisenhower Institute National Advisory Council). Members of the EINAC include the granddaughter of a past U.S. president, the president of Gettysburg College, a member of the 9/11 Commission, and other notable donors and alumni.
\end{itemize}
%end section

\section*{Presentations (\url{http://cs.gettysburg.edu/\textasciitilde duncjo01/assets/about.html})}
\subsection*{Talks}
\begin{itemize}[noitemsep]
	\item Socratic Club Seminar (future of work) \hfill \textit{Spring 2017}
	\item Computer Science Capstone Colloquium \hfill \textit{Fall 2016}
	\item Internship Colloquium \hfill \textit{Spring 2016}, \textit{Fall 2016}
	\item Computer Science Department ``Get Acquainted Day'' \hfill \textit{Spring 2016}
	\item Hitchhiker's Guide to Computer Science Colloquium \hfill \textit{Fall 2015/2016}, \textit{Spring 2016}
	\item Gettysburg College Celebration \hfill \textit{Spring 2015/2017}
\end{itemize}

\subsection*{Planned/Moderated}
\begin{itemize}[noitemsep]
	\item Programming Competition Colloquium \hfill \textit{Spring 2017}
	\item Student Solidarity Rally \hfill \textit{Spring 2017}
	\item EI Panel: Lady Liberty's Poor and Huddled Masses: \textit{Rethinking Refugees in America} \hfill \textit{Spring 2017}
	\item EI Panel: We Want You...Or Do We? \textit{A Panel on Refugees \& Asylees Coming to the U.S.} \hfill \textit{Fall 2016}
	\item We Won't Stand for Hate at Gettysburg College \hfill \textit{Fall 2016}
	\item Political Debates \hfill \textit{Fall 2015/2016}, \textit{Spring 2016}
	\item Hour of Code Colloquia \hfill \textit{Fall 2015/2016}
\end{itemize}
%end section

\section*{Governance}
\subsection*{Gettysburg Association for Computing Machinery (ACM) chapter}
\begin{itemize}[noitemsep]
	\item Vice President \hfill \textit{2016-2017}
	\item Secretary \hfill \textit{2015-2016}
	\item Student Senate Representative \hfill \textit{2015-2017}
	%\item Attended weekly student senate meetings as a club representative \hfill 2015-2017
\end{itemize}
 
\subsection*{Gettysburg College Independents} 
\begin{itemize}[noitemsep]
	\item Treasurer \hfill \textit{2016-2017}
    \item Organized and moderated three political debates between the College Democrats and College Republicans. 
\end{itemize}

\subsection*{Gettysburg Anti-Capitalist Collective (GACC)}
\begin{itemize}[noitemsep]
    \item Political organization. Organized debates, events \& rallies, distributed zines, and participated in campus activism projects. Club also served as a welcoming space for politically and socially marginalized LGBTQA+ students.
    \item Student Senate Representative \hfill \textit{2016-2017}
\end{itemize}
%end section

%\section*{Languages}
%\begin{tabular}{ | c | c | }
%	\hline
%	English & native \\ 
%	\hline
%	French & proficient (written and spoken) \\  
%	\hline
%	Spanish & elementary (101 and 102) \\
%	\hline
%\end{tabular}
%end section

\section*{References}
Contact information for references available upon request. \\

\begin{tabular}{ l l l }
	\textbf{Charles E. Rose} & \textit{Associate Technical Staff} & MIT Lincoln Laboratory \\
	\textbf{Dr. Todd W. Neller} & \textit{Professor} & Gettysburg College Computer Science Dept. \\
	\textbf{Dr. Lisa Portmess} & \textit{Bittinger Professor of Philosophy} & Gettysburg College Philosophy Dept. \\
	\textbf{Dr. Shirley Anne Warshaw} & \textit{Professor} & Gettysburg College Political Science Dept. \\
	\textbf{Dr. Charles W. Kann, III} & \textit{Adjunct Professor} & Johns Hopkins Whiting School of Engineering \\
\end{tabular}
%end section

\end {document}